RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-06-03 rmd/manuscript.Rmd
edit: minor

\*Corresponding Author: JPF Pomeranz, [jfpomeranz\@gmail.com](mailto:jfpomeranz@gmail.com){.email}; A Terui, [hanabi0111\@gmail.com](mailto:hanabi0111@gmail.com){.email}

@@

Understanding the drivers of food chain length in natural communities has intrigued ecologists since Elton publicized 'food cycles' in the early 20th century. Proposed drivers of food chain length have included productivity, disturbance regime, ecosystem size, and trophic omnivory. However, current theories have largely assumed simple, two-dimensional habitat architectures and may not be adequate to predict food chain length in ecosystems with a complex, branching structure. Here, we develop a spatially explicit theoretical model which provides an integrated framework for understanding variation in food chain length in branching networks. We show independent, positive influences of ecosystem size and complexity on food chain length. However, the effects of ecosystem size and complexity were contingent upon other factors, appearing more clearly in high-disturbance and high-productivity regimes. Our results suggest that ecosystem complexity is an important yet overlooked driver of food chain length that may increase the resilience to anthropogenic environmental changes.

@@

# References{-}

<div id="refs"></div>

>>>>

\*Corresponding Author: A Terui, [hanabi0111\@gmail.com](mailto:hanabi0111@gmail.com){.email}

@@

Understanding the drivers of food chain length in natural communities has intrigued ecologists since Elton publicized 'food cycles' in the early 20th century. Proposed drivers of food chain length have included productivity, disturbance regime, ecosystem size, and trophic omnivory. However, current theories have largely assumed simple, two-dimensional habitat architectures and may not be adequate to predict food chain length in ecosystems with a complex, branching structure. Here, we develop a spatially explicit theoretical model which provides an integrated framework for understanding variation in food chain length in branching networks. We show independent, positive influences of ecosystem size and complexity (as indicated by branching properties) on food chain length. However, the effects of ecosystem size and complexity were contingent upon other factors, appearing more clearly in high-disturbance and high-productivity regimes. Our results suggest that ecosystem complexity is an important yet overlooked driver of food chain length that may increase the resilience to anthropogenic environmental changes.

@@

# References {.unnumbered}

::: {#refs}
:::

### 2023-06-03 rmd/reply2.Rmd
edit: minor

> We also encourage you to review our response to your previous comments, as it provides additional information related to the definition and dynamics of FCL in our study.

>>>>

> We also encourage you to review our response to your earlier comments in this letter, as it provides additional information related to the definition and dynamics of FCL in our study.
